Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
chore: minors

%% Put three subfigures of simulations, start, after, end
\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/start.png}
      \caption{Initial state}
      \label{fig:initial}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/after.png}
      \caption{After 50 steps}
      \label{fig:after}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/end.png}
      \caption{After 200 steps}
      \label{fig:end}
  \end{subfigure}
  \caption{Simulation of the proposed approach. 
  The dots represent the robots, 
  the circle area on the top right represent the phenomenon to be monitored, 
  and the gray area represent the area covered by the robots.}
  \label{fig:simulations}
\end{figure}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal. The individual agents do not have any knowledge of the initial phenomenon itself (i.e., shape, size, location, velocity,...).
 \lukas{``Initially we consider a stationary phenomenon before expanding towards a moving phenomenon. Additionally, the phenomenon can change its shape during runtime. Finally, the phenomenon may have varying areas of interest, defined by an underlying distribution function. Figure~\ref{fig:simulations} illustrates a set of 25 agents and a single, stationary phenomenon with a with a 3D Gaussian distribution.''}

>>>>

%% Put three subfigures of simulations, start, after, end
\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/start.png}
      \caption{Initial state}
      \label{fig:initial}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/after.png}
      \caption{After 50 steps}
      \label{fig:after}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\linewidth}
      \includegraphics[width=\textwidth]{imgs/end.png}
      \caption{After 200 steps}
      \label{fig:end}
  \end{subfigure}
  \caption{Simulation of the proposed approach. 
  The dots represent the robots, 
  the circle area on the top right represents the phenomenon to be monitored, 
  and the grey area represents the area covered by the robots.}
  \label{fig:simulations}
\end{figure}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal. The individual agents do not have any knowledge of the initial phenomenon itself (i.e., shape, size, location, velocity,...).
 \lukas{``Initially we consider a stationary phenomenon before expanding towards a moving phenomenon. Additionally, the phenomenon can change its shape during runtime. Finally, the phenomenon may have varying areas of interest, defined by an underlying distribution function. Figure~\ref{fig:simulations} illustrates a set of 25 agents and a single, stationary phenomenon with a with a 3D Gaussian distribution.''}
